---
output: html_document
editor_options: 
chunk_output_type: console
---

# Results

We finally reach the stage where we will be performing the actual analysis and solve the questions we presented in the Problem Statement at the start. We have divided this analysis into three broader segments and will be presenting objectives and outputs as we go along.


```{r echo=FALSE, message=FALSE, warning=FALSE}
library(prophet)
library(quantmod)
library(forecast)
library(tseries)
library(timeSeries)
library(plyr)
library(dplyr)
library(fGarch)
library(ggplot2)
library(plotly)
library(DescTools)
library(PerformanceAnalytics)
library(dygraphs)
library(makeR) # must be installed from source
library(tidyquant)
```



## Analysis of Repetitive Patterns

Let us start the analysis by studying the overall global picture that the coronavirus painted across all major stock markets. In the analysis below, we study about seven equity markets spread on the globe.

- FTSE (London, United Kingdom) - The Financial Times Stock Exchange 100 Index, also called the FTSE 100 Index, FTSE 100, FTSE, or, informally, the "Footsie", is a share index of the 100 companies listed on the London Stock Exchange with the highest market capitalisation.
- DAX (Frankfurt, Germany) - The DAX is a representation of the German (Frankfurt) Stock Exchange consisting majorly of the Bluechip organizations trading in Germany.
- FEZ (Europe on New York Stock Exchange) - The FEX equity holds European stocks on the NYSE. This is, therefore, a unique equity to understand since it functions on cross-market sentiments.
- 000001.SS - SSE Composite Index (Shanghai, China) - The SSE index is a representation of the Shanghai Stock Exchange and trades equities in the Chinese markets.
- IXIC - Nasdaq Composit (United States) - The Nasdaq Composite is a stock market index that includes almost all stocks listed on the Nasdaq stock exchange. Along with the Dow Jones Industrial Average and S&P 500, it is one of the three most-followed stock market indices in the United States.
- DJI (United States) - Dow Jones Industrial Average
- N225 - Nikkei (Tokyo, Japan) - The Nikkei 225, or the Nikkei Stock Average, more commonly called the Nikkei or the Nikkei index, is a stock market index for the Tokyo Stock Exchange.


```{r Plot 1,echo=FALSE, results='asis', fig.width=8, fig.height=8}

a = returns('^FTSE', 2019)
b = returns('DAX', 2019)
c = returns('FEZ', 2019)
d = returns('000001.SS', 2019)
e = returns('^IXIC', 2019)
f = returns('^DJI', 2019)
g = returns('^N225', 2019)

merged_returns_two <- merge.xts(a, b, c, d, e, f, g)
merged_returns_two <- na.omit(merged_returns_two) 

dygraph(merged_returns_two, main = "Global Market Trends") %>%
  dyAxis("y", label = "Returns") %>%
  dyOptions(stackedGraph = TRUE)
```


**Key Observations from the analysis of Global Markets:**

1. The foremost observation this graph gives us is the sudden fall in returns in April 2020. This was one of the biggest falls in US and the gloab Stock Market History and came just the day after WHO announced COVID-19 as a global pandemic.
2. Again, in December 2020 - January 2021 we see a sudden high upside in all the returns. This was the moment when pharmaceuticals in Russia and the United States had announced their progress of vaccine programs.
3. A common and not-so-expected trend we see is that all the major global markets followed the same trend throughout COVID-19. The same degree of fall and rise on all accounts. A question arises here, are all global markets always (regardless of any events) follow similar patterns of growth and demand?

**Day Trade Patterns during the announcement of the Covid Outbreak and Vaccine Availability**

Let us now look at the trading prices of some diversified sectors of economy to understand if we see any important patterns of data.

```{r Plot2, results='asis', fig.height=8, fig.width=8}

library("readxl")
library(tidyr)
library(reshape2)
library(ggplot2)
library(scales)

close_price <- read_excel("data/Processed/ClosePrice.xlsx")
close_price$Date <- as.Date(close_price$Date)

ggplot(data = close_price, aes(x = close_price$Date)) +
  geom_line(aes(y = close_price$Tesla, colour = "Tesla")) +
  geom_line(aes(y = close_price$Pfizer, colour = "Pfizer")) +
  geom_line(aes(y = close_price$Moderna, colour = "Moderna")) +
  geom_line(aes(y = close_price$Apple, colour = "Apple")) +
  geom_line(aes(y = close_price$Johnson_Johnson, colour = "Johnson_Johnson")) +
  geom_line(aes(y = close_price$Goldman_Sachs, colour = "Goldman_Sachs")) +
  geom_line(aes(y = close_price$`Archer-Daniels-Midland`, colour = "`Archer-Daniels-Midland")) +
  geom_line(aes(y = close_price$CVS_Health, colour = "CVS_Health")) +
  geom_line(aes(y = close_price$Ørsted, colour = "Ørsted")) +
  scale_colour_manual("", 
                      breaks = c("Tesla", 
                                 "Pfizer", 
                                 "Moderna",
                                 "Apple",
                                 "Johnson_Johnson",
                                 "Goldman_Sachs",
                                 "`Archer-Daniels-Midland",
                                 "CVS_Health",
                                 "Ørsted"),
                      values = c("Tesla"="red", 
                                 "Pfizer"="pink", 
                                 "Moderna"="azure",
                                 "Apple"="orange",
                                 "Johnson_Johnson"="yellow",
                                 "Goldman_Sachs"="blue",
                                 "`Archer-Daniels-Midland"="magenta",
                                 "CVS_Health"="violet",
                                 "Ørsted"="grey")) +
  xlab("Date") +
  scale_y_continuous("Close Prices") + 
  scale_x_date(date_breaks = "1 month", date_labels =  "%b %Y") +
  labs(title="Day Trading impacts on announcement of COVID and Availability of Vaccines") +
  theme(axis.text.x=element_text(angle=60, hjust=1)) +
  geom_vline(xintercept = as.numeric(as.Date("2019-12-01"), linetype=4)) +
  geom_vline(xintercept = as.numeric(as.Date("2020-11-09"), colour="green", linetype = "longdash"))

```

**Key Observations from the analysis of Global Markets:**

1. The first observation from this analysis is that the performance of organizations did not get affected by the advent of the virus starting to spread in China, which is represented by the first black verticle line. 
2. The steep decline only started after WHO officially declared COVID-19 a pandemic in March 2020. This stands with the observation we made above. 
3. The second black vertical represents the annoucement of vaccine preparation and despatch and we see a rise soon after that point in almost all the stocks.
4. A surprising note is that Johnson & Johnson and Pfizer stayed constant throughout COVID-19 despite all the news. It explains that the investor's sentiment did not align with vaccine news. 

## Behavioural Stock Price Analytics during COVID-19

```{r Data Prep}
# Data Preparation

Pfizer = getSymbols("PFE", src="yahoo", from="2019-09-01", to="2021-12-10", auto.assign=FALSE)
Pfizer = data.frame(date = index(Pfizer), Pfizer, row.names=NULL)
colnames(Pfizer) <- c('Date', 'Open','High','Low', 'Close', 'Volume', 'Adjusted')
Pfizer = cbind(Pfizer,Stock="")
Pfizer$Stock = paste(Pfizer$Stock,"Pfizer",sep="")

Moderna = getSymbols("MRNA", src="yahoo", from="2019-09-01", to="2021-12-10", auto.assign=FALSE)
Moderna = data.frame(date = index(Moderna), Moderna, row.names=NULL)
colnames(Moderna) <- c('Date','Open','High','Low', 'Close', 'Volume', 'Adjusted')
Moderna = cbind(Moderna,Stock="")
Moderna$Stock = paste(Moderna$Stock,"Moderna",sep="")

Johnson_Johnson = getSymbols("JNJ", src="yahoo", from="2019-09-01", to="2021-12-10", auto.assign=FALSE)
Johnson_Johnson = data.frame(date = index(Johnson_Johnson), Johnson_Johnson, row.names=NULL)
colnames(Johnson_Johnson) <- c('Date', 'Open','High','Low', 'Close', 'Volume', 'Adjusted')
Johnson_Johnson = cbind(Johnson_Johnson,Stock="")
Johnson_Johnson$Stock = paste(Johnson_Johnson$Stock,"Johnson_Johnson",sep="")

Prudential_Insurance = getSymbols("PRU", src="yahoo", from="2019-09-01", to="2021-12-10", auto.assign=FALSE)
Prudential_Insurance = data.frame(date = index(Prudential_Insurance), Prudential_Insurance, row.names=NULL)
colnames(Prudential_Insurance) <- c('Date', 'Open','High','Low', 'Close', 'Volume', 'Adjusted')
Prudential_Insurance = cbind(Prudential_Insurance,Stock="")
Prudential_Insurance$Stock = paste(Prudential_Insurance$Stock,"Prudential_Insurance",sep="")

CVS_Health = getSymbols("CVS", src="yahoo", from="2019-09-01", to="2021-12-10", auto.assign=FALSE)
CVS_Health = data.frame(date = index(CVS_Health), CVS_Health, row.names=NULL)
colnames(CVS_Health) <- c('Date', 'Open','High','Low', 'Close', 'Volume', 'Adjusted')
CVS_Health = cbind(CVS_Health,Stock="")
CVS_Health$Stock = paste(CVS_Health$Stock,"CVS_Health",sep="")

Walgreens_Boots = getSymbols("WBA", src="yahoo", from="2019-09-01", to="2021-12-10", auto.assign=FALSE)
Walgreens_Boots = data.frame(date = index(Walgreens_Boots), Walgreens_Boots, row.names=NULL)
colnames(Walgreens_Boots) <- c('Date', 'Open','High','Low', 'Close', 'Volume', 'Adjusted')
Walgreens_Boots = cbind(Walgreens_Boots,Stock="")
Walgreens_Boots$Stock = paste(Walgreens_Boots$Stock,"Walgreens_Boots",sep="")

Master_Data = rbind(Pfizer, Moderna, Johnson_Johnson, Prudential_Insurance, CVS_Health, Walgreens_Boots)
```

One metric that helps us understand the behaviour of investing is the number of trades being executed during day trades. The trade volume for all the stocks will tell us if trade executions increased post some key announcements.

```{r Plot 3, results='asis', fig.height=8, fig.width=8}

ggplot(data = Master_Data, aes(x = Date, y = Volume)) +
  geom_segment(aes(xend = Date, yend = 0, color = Volume)) + 
  labs(title = "Trading Volumes Chart", 
     subtitle = "Daily Trades Volumes highlighting 2 days - COVID pandemic Annoucement and Vaccine Building Annoucement", 
     y = "Volume", x = "") +
  theme_tq() +
  facet_wrap(~ Stock) +
  geom_vline(xintercept = as.numeric(as.Date("2019-12-01"), linetype=4)) +
  geom_vline(xintercept = as.numeric(as.Date("2020-11-09"), colour="green", linetype = "longdash")) +
  theme(legend.position = "none") 
```

**Trading Volumnes through COVID-19**

1. Pfizer and Moderna are two stocks that saw steep rises during the annoucement of their respective vaccine programs. 
2. We do not see any other significant movement on other market segments during this time which coincides with the analysis we have done so far. 


```{r Plot4, echo=FALSE, results='asis', fig.width=8, fig.height=8}

library(tidyr)
library(stringr)

k <- 1:450
col_names <- paste0("lag_", k)

## Only Select Columns "Date" and "Close" from hte master data frame.

Master_Data_lags<-Master_Data%>%
tibble::as_tibble() %>%
group_by(Stock)

Master_Data_lags<-Master_Data_lags%>%select(Date,Close)
# Apply lag.xts function using tq_mutate

Master_Data_lags<-Master_Data_lags%>%
tq_mutate(
select = Close,
mutate_fun = lag.xts,
k=1:450,
col_rename=col_names
)

# Calculate the autocorrelations and 95% cutoffs

Master_Data_AutoCorrelations<-Master_Data_lags %>%
gather(key = "lag", value = "lag_value", -c(Stock,Date, Close)) %>%
mutate(lag = str_sub(lag, start = 5) %>% as.numeric) %>%
group_by(Stock, lag) %>%
summarize(
cor = cor(x = Close, y = lag_value, use = "pairwise.complete.obs"),
cutoff_upper = 2/(n())^0.5,
cutoff_lower = -2/(n())^0.5
)

## Visualisation of Autocorrelation: ACF Plot

Master_Data_AutoCorrelations %>%
ggplot(aes(x = lag, y = cor, color = Stock, group = Stock)) +

# Add horizontal line a y=0
geom_hline(yintercept = 0) +

# Plot autocorrelations
geom_point(size = 2) +
geom_segment(aes(xend = lag, yend = 0), size = 1) +

# Add cutoffs
geom_line(aes(y = cutoff_upper), color = "blue", linetype = 2) +
geom_line(aes(y = cutoff_lower), color = "blue", linetype = 2) +

# Add facets
facet_wrap(~ Stock, ncol = 3) +

# Aesthetics
expand_limits(y = c(-1, 1)) +
scale_color_tq() +
theme_tq() +
labs(
title = paste0("ACF Plot: Lags ", rlang::expr_text(k)),
x = "Lags"
) +
theme(
legend.position = "none",
axis.text.x = element_text(angle = 45, hjust = 1),
panel.grid.major = element_line(colour = "grey61", size = 0.5, linetype = "dotted"),
plot.title = element_text(hjust = 0.5,size=18,colour="indianred4")
)
```

**Plotting stock prices against 450 lag orders**

1. Moderna is one stock that does shows a positive lag order throughout the time series signifying that prices were always unidirectional and were not affected by any of the events we discussed.
2. All the other stocks do not show any significant patterns of upward or downward flow.

## Comparison of Vaccine Developing companies against others

- Pfizer (Ticker: PFE)
- BioNTech (Ticker: BNTX)
- Moderna (Ticker: MRNA)
- Johnson & Johnson (Ticker: JNJ)

Comparison against

- S&P 500 (Ticker: ^GSPC)
- Dow Jones Industrial Average (Ticker: ^DJI)
- Nasdaq Composite (Ticker: ^IXIC)
- United Parcel Service (Ticker: UPS)
- Toyota Motor Corporation (Ticker: TM)

```{r}
returns <- function(ticker, start_year) {
  symbol <- getSymbols(ticker, src = 'yahoo', auto.assign = FALSE, warnings = FALSE)
  data <- periodReturn(symbol, period = 'monthly', subset=paste(start_year, "::", sep = ""), type = 'log')
  colnames(data) <- as.character(ticker)
  assign(ticker, data, .GlobalEnv)
}

returns('PFE', 2019)
returns('BNTX', 2019)
returns('MRNA', 2019)
returns('JNJ', 2019)
g = returns('^GSPC', 2019)
d = returns('^DJI', 2019)
returns('UPS', 2019)

merged_returns <- merge.xts(PFE, BNTX, MRNA, JNJ, g, d, UPS)
```

```{r Plot5, echo=FALSE, results='asis'}

dygraph(merged_returns, main = "Comparision of Returns") %>%
  dyAxis("y", label = "Return Percentage") %>%
  dyOptions(colors = RColorBrewer::brewer.pal(7, "Set2"))

```

Observations from the chart above:
- Pfizer, Moderna, Johnson & Johnson and BioNTech were the companies that announced their vaccine development programs early in 2021. 
- In the period from November 2020 to February 2021, we see a drastic volatility in two of those four stocks, namely, Moderna and BioNTech. 
- One anticipation for this result might be that BioNTech was actually co-developing the vaccine with Pfizer where Pfizer's role was to meet with production demands.
- Johnson & Johnson was very late to the development and therefore, there is no volatility in it's stock.

